---
title: "MATH  4753 functions from lab"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MATH  4753 functions from lab}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>" 
)
```

```{r setup}
library(MATH4752Projects1)
```



# Introduction
This package consist of four functions and a file named fire. The three functions are, mybin which makes a table and barplot for a binomial simulation. The Myf function makes a square root function. The myci function returns a 95% confidence interval.  Lastly the myncurve function makes normal curve probability and shades the required area. 

# mybin
mybin=function(iter=100,n=10, p=0.5){

  sam.mat=matrix(NA,nr=n,nc=iter, byrow=TRUE)

  succ=c()
  for( i in 1:iter){

    sam.mat[,i]=sample(c(1,0),n,replace=TRUE, prob=c(p,1-p))

    succ[i]=sum(sam.mat[,i])
  }

  succ.tab=table(factor(succ,levels = 0:n))

  iter.lab =paste0("iter =", iter)
  n.lab = paste0("n = ", n)
  p.lab = paste0("p =", p)
  lab= paste(iter.lab,p.lab,sep = ", ")


  barplot(succ.tab/(iter), col=rainbow(n+1), main="Binomial simulation", xlab="Number of successes")
  succ.tab/iter
}

# myf
myf=function(x){
  x^2
}

# myci
myci<- function(x){
  n<-length(x)
  std <- sd(x)
  t<-qt(1-0.05/2,n-1)
  mp <- c(-1,1)
  mean(x)+ mp*t*std/sqrt(n)

}

# mycurve
myncurve = function(mu, sigma, a){
  bottom=mu-3*sigma
  top=mu+ 3*sigma
  curve(dnorm(x,mean=mu,sd=sigma), xlim = c(bottom, top))
  xcurve=seq(bottom,a,length=1000)
  ycurve=dnorm(xcurve,mean=mu,sd=sigma)
  polygon(c(bottom,xcurve,a),c(0,ycurve,0),col="Red")

  prob=pnorm(a,mean=mu,sd=sigma)-pnorm(bottom,mean=mu,sd=sigma)
  prob=round(prob,4)
  text(a,dnorm(a,mu,sigma), paste0("Area = ", prob,sep=""))

}



